Lower Bounds on the Minimax Risk for the \\ Source Localization Problem

### 2017-02-06 paper.tex
Add acknowledgements and complete appendix.

@@

>>>>

\section*{Acknowledgements}

This work was supported in part by Systems on Nanoscale Information fabriCs
(SONIC), one of the six SRC STARnet Centers, sponsored by MARCO and DARPA.
Praveen Venkatesh was supported (in part) by the Dowd Fellowship from the
College of Engineering at Carnegie Mellon University. The authors would like to
thank Philip and Marsha Dowd for their financial support and encouragement.

@@

In the integrator model of sensors, recall that the samples are given by
equation~\eqref{eq:samples-int-model}. We compute the SNR approximately at the
$k$-th sensor as follows. The power of the signal is given by
\begin{align}
	\abs{x_k(\theta)}^2 &= \bigg(\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} x(s;\theta) ds\bigg)^2 \\
	&\approx \bigg(\frac{S}{m} \; x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 = \frac{S^2}{m^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \label{eq:signal-power-k},
\end{align}
where in the approximation, we have assumed that the signal is roughly constant
in a small interval, taking the value of the signal at $s = kS/m$. The constant
itself is not relevant; it suffices to note at this point that the signal power
diminishes as $1/m^2$ since the sensor size \emph{must} diminish as $1/m$, if
the number of sensors has to increase to infinity.

The noise variance at the $k$-th sensor is computed similarly:
\begin{align}
	\mathbb E[\epsilon_k^2] &= \mathbb E \Bigg[ \bigg(\int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s)\bigg)^2 \Bigg] \\
	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s) ds \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s') ds' \Bigg] \\
	&= \mathbb E \Bigg[ \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \epsilon(s) \epsilon(s') ds ds' \Bigg] \\
	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \mathbb E[\epsilon(s) \epsilon(s')] ds ds' \\
	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} R_\epsilon(s, s') ds ds' \\
	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \sigma^2 \delta(s - s') ds ds' \\
	&= \int_{(k-\frac{1}{2})S/m}^{(k+\frac{1}{2})S/m} \sigma^2 ds \\
	&= \sigma^2 \frac{S}{m}, \label{eq:noise-var-k}
\end{align}
where $R_\epsilon(s, s') = \sigma^2 \delta(s - s')$ is the autocorrelation
function of the white noise process, and $\sigma^2$ is the amplitude of the
white noise power spectral density.

We can understand how the SNR at the $k$-th sensor scales with $m$, therefore,
by taking the ratio of~\eqref{eq:signal-power-k} and~\eqref{eq:noise-var-k}
\begin{align}
	\text{SNR}(k) &= \frac{S^2}{m^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \cdot \frac{m}{S\sigma^2} \\
	&= \frac{S}{m\sigma^2} \bigg(x\Big(\frac{kS}{m}; \theta\Big)\bigg)^2 \propto 1/m.
\end{align}
Hence, as the number of sensors $m$ grows to infinity, their sizes must
necessarily reduce inversely with $m$, and as a result, their SNR also falls
inversely with $m$, when we view these sensors as integrators.
